### 2015-01-17 src/introduction.Rnw
add more references

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only a small fraction of randomly selected mutants.
Wong and Mathur found that random sampling fraction as low as 10\%
could provide accurate results~\cite{jia2011analysis}.

>>>>

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only a small fraction of randomly selected mutants.
Wong and Mathur found that random sampling fraction as low as 10\%
could provide accurate results~\cite{jia2011analysis}, and was recently
found that it increases at a rate of $O(x^{\frac{1}{4}})$ when program
size increases linearly~\cite{zhang2014empirical}.
